Investigating Biases Associated with Dietary Starch Incorporation and Retention with an Oral Biofilm Model

### 2024-01-04 analysis/paper/results.qmd
fix: convert cross-refs to quarto and add figures and tables

Pearson's *r* suggests a 
`r strength_cor` `r direct_cor` 
correlation between the total weight of the biofilms and the total starch count 
(standardised by z-score) extracted from the samples across treatments, 
*r* = `r cor_r`, 
90%CI[`r paste(cor_ci[1], cor_ci[2], sep = ", ")`],
p `r cor_p`
(Figure \@ref(fig:cor-plot)A).

The same test was applied to total biofilm weight and starch count per mg 
calculus (also standardised by z-score), resulting in a weak positive correlation, 
*r* = `r cor2_r`, 
90%CI[`r paste(cor2_ci[1], cor2_ci[2], sep = ", ")`],
p `r cor2_p`
(Figure \@ref(fig:cor-plot)B).

>>>>

Pearson's *r* suggests a 
`r strength_cor` `r direct_cor` 
correlation between the total weight of the biofilms and the total starch count 
(standardised by z-score) extracted from the samples across treatments, 
*r* = `r cor_r`, 
90%CI[`r paste(cor_ci[1], cor_ci[2], sep = ", ")`],
p `r cor_p`
([@fig-cor-plot]A).

```{r}
#| label: fig-cor-plot
#| warning: false
#| fig-cap: "Scatter plots of (A) sample weight in mg and standardised starch count by z-score for separated treatments, and (B) sample weight in mg and standardised count of starch grains per mg calculus."

pl_cor + pl_cor2 + plot_layout(guides = "collect") + plot_annotation(tag_levels = "A")
```

The same test was applied to total biofilm weight and starch count per mg 
calculus (also standardised by z-score), resulting in a weak positive correlation, 
*r* = `r cor2_r`, 
90%CI[`r paste(cor2_ci[1], cor2_ci[2], sep = ", ")`],
p `r cor2_p`
([@fig-cor-plot]B).
